### 2013-02-19 hw4/document/hw4.tex
The tex document

\documentclass{article}

\usepackage{fullpage}
\usepackage{graphicx}

\title{Homework 4}
\author{Caius Brindescu \and Mihai Codoban \and Semih Okur \and Shao Yuan \and Kyungho Leoo}

\begin{document}

\maketitle

\begin{figure}
	\begin{center}
		\includegraphics{image.jpg}
	\end{center}
	\caption{The image we used}
	\label{fig:image}
\end{figure}

\begin{figure}
	%%\includegraphics{cloud.png}
	\caption{The word cloud}
	\label{fig:cloud}
\end{figure}

\begin{enumerate}

\item What programming environment did you use? What did you use for generating the word cloud?

We used Java and Eclipse for interacting with the Mechanical Turk and Python for generating the word cloud.

\item Where did the visual design come from and why did you choose it?

\item How many workers were involved in producing the final word cloud?

50.

\item What was the total labor cost for producing the word cloud? Don't include the costs related to any earlier experimentation.

\$1.00

\item How long did it take to produce the word cloud (i.e. from the time the program was started to when the word cloud was returned)?

If this includes the time it took for the tasks to be completed, about  a day. If it refers only for the time needed to compute the word cloud, then it was less than 1 second.

\item Diagram the overall workflow or process that you implemented to produce the word cloud.

\item How would you characterize the quality of the first impressions captured by the word cloud?

\item How did the first impressions returned by the crowd match or deviate from your group's expectations for the design?

Since it was an abstract piece of art, we did not have particular expectations. Wer

\item Describe some ways that might improve the efficiency or outcomes of the task? For example, how could you achieve a higher quality outcome; or how could you reduce the number of workers required, the total labor costs, or the time required to produce an outcome of the same quality?

\item From the perspective of the designer who created the design used in the project, how might being able to collect first impressions from potential users benefit the design process?

\end{enumerate}

\end{document}

### 2013-02-19 hw4/document/hw4.tex
filled in the remaining homework questions

@@
 
+We choose an abstract painting from Picasso because we were interested in seeing what concepts different people see in a work of art in which the main message is suggested, hinted upon, rather than revealed upfront.
+
 \item How many workers were involved in producing the final word cloud?
@@
 
+We got a java word cloud from GitHub (epicdevs/Word-Cloud). It takes a list of strings as input and outputs a BufferedImage which we flushed to file as a PNG.
+
 \item How would you characterize the quality of the first impressions captured by the word cloud?
+
+We got an interesting blend of concepts. Initially we assumed that \emph{music}, \emph{sentiment} or \emph{melange} would be among of the top hits.
 
@@
 
-Since it was an abstract piece of art, we did not have particular expectations. Wer
+Since it was an abstract piece of art, we did not have particular expectations. They could have either converged to a core of concepts, or could have yielded unique results.
 
@@
 
+Insted of using only one image, we could use a batch of different images built around the same concept.
+
 \item From the perspective of the designer who created the design used in the project, how might being able to collect first impressions from potential users benefit the design process?
+
+By getting first impressions, we align ourselves with the global perception.
+When working in the studio, it is easy to get a skewed perception, to derail from the global train of thought.
+By getting valuable feedback from the outsied, we align ourselves once more with reality.
 

### 2013-02-19 hw4/document/hw4.tex
Added the word cloud
Fixed minor stuff

@@
 \title{Homework 4}
-\author{Caius Brindescu \and Mihai Codoban \and Semih Okur \and Shao Yuan \and Kyungho Leoo}
+\author{Caius Brindescu \and Mihai Codoban \and Semih Okur \and Shao Yuan \and Kyungho Lee}
 
@@
 
-\begin{figure}
+\begin{figure}[hbt]
 	\begin{center}
@@
 
-\begin{figure}
-	%%\includegraphics{cloud.png}
+\begin{figure}[hbt]
+	\includegraphics[width=\textwidth]{wordcloud.png}
 	\caption{The word cloud}
@@
 
+As the word cloud shows, it actually converged to the core concept.
+
 \item Describe some ways that might improve the efficiency or outcomes of the task?
@@
 When working in the studio, it is easy to get a skewed perception, to derail from the global train of thought.
-By getting valuable feedback from the outsied, we align ourselves once more with reality.
+By getting valuable feedback from the outside, we align ourselves once more with reality.
 

### 2013-03-05 proposal/proposal.tex
Added the proposal

\documentclass[titlepage,twopage]{article}

\usepackage{graphicx}
\usepackage{hyperref}

\newcommand{\rarrow}{$\rightarrow$}

\title{Guide Map to Learn a Programming Language Generated by Crowd Insights}
\author{Mihai Codoban \and Caius Brindescu \and Semih Okur \and Kyungho Lee \and Shuo Yuan}

\begin{document}

\maketitle

\section*{Document history}

\begin{tabular}{| l | l | p{8cm} |}
\hline
\textbf{Date} & \textbf{Author} & \textbf{Comments} \\ \hline \hline
February 28, 2013 & Lee & Wrote the first draft, consulted with Prof. Bailiey \\ \hline 
February 28, 2013 & Lee & Put 3 figures to explain our concept \\ \hline
February 31, 2013 & Mihai & Added tool description \\ \hline
March 4, 2013 & Janus & Added Related Work section \\ \hline
March 4, 2013 & Mihai & Added reference \cite{mayer1981psychology} and detailed it at the start of section~\ref{sec:prelim-work}\\ \hline
March 5, 2013 & Semih & Detailed the map function and added reference \cite{okur2012developers} \\ \hline
March 5, 2013 & Caius & Made \LaTeX{} version \\ \hline
\end{tabular}

\cleardoublepage

\section{Project Summary}

Many people struggle with learning a programming language to create digital artifacts. Due to difficulties that people experience from programming, people might lose an opportunity to contribute to express their creativity for evolutionary innovations toward the society. In this regard, this research aims to design a creativity support tool for generating a “guide map to learn a programming language” made by valuable insights from crowds -- people who already experienced the same problems and learning process.

This research aims to:
\begin{itemize}
\item Observe students and teaching assistants (CS major, Art and Design major) to find major difficulties to learn a programming language in terms of learning process.
\item Find diverse opportunities to design an appropriate interface, which is functioning as a map for learning, for people (both of novices and experts).
\item Conduct crowdsourcing through online and offline to get sufficient insights, processes, tips, and useful resources to generate a map from diverse perspectives and backgrounds.
\item Build infrastructures and interfaces that enable people to engage and get real insights from a map generated by crowds so that the accelerate their learning process
\item Measure performances, conduct a post interview and analyze the results through a statistical methods to analyze the goal, objectives and impact of the tool 
\end{itemize}

\section{Project Description}

\begin{quote}
``Everybody in this country should learn how to program a computer because it teaches you how to think'' -- Steve Jobs
\end{quote}

A video, ``What most schools don't teach,'' circled the Internet this week. In it, a stream of renowned figures in the software world, such as, Microsoft, Dropbox, Facebook, and Twitter, make a compelling case for why everyone should learn how to program. This clip once again stresses the importance of programming; authors consider creating through programming is a vibrant way of expressing creativity in this generation \cite{winslow1996programming}.

Researchers in the science education field regard the behavior of programmers and get results from them as an information problem solving process that involves cognitive and metacognitive issues; they believe that programming techniques and skills that are not easily acquired \cite{lazonder2008information}.

Unfortunately, most of people who have not sufficient background in the science or engineering would drop out of learning programming when they get stuck in a certain phase of their journey; those frustrating experiences prevent people from creating valuable artifacts or enabling evolutionary innovations \cite{pane1996usability}.

There are several reasons that hinder people from effective and efficient learning how to program. According to survey, one of biggest challenge for people to learn programming languages is a lack of understanding about an overall concept of the programming language that they wanted to use. The other challenges that they encounter are building functions and looping them within their program. After that, people would struggle with using libraries and input/output handling  \cite{lahtinen2005study}.

Another research also shows that these problematic experiences were observed not only within students whose background is not science or engineering but also happened for students whose major is computer science. (Murphy et al., 2006) It clearly shows that learning programming is not easy. Upon this, we empirically know that many novice programmers get lost in their way when they try to learn a new programming language by themselves \cite{milne2002difficulties}.

In this regard, we will design a creativity support tool that provides a guide map for people to get a holistic concept of the language so that they accelerate in learning a programming language by avoiding common pitfalls; the map will be generated by crowds’ participation so that we could collect valuable insights, common pitfalls to avoid, useful links, source code and so forth. This project is initiated based on four what-if questions:
\begin{enumerate}
\item What if we can get a big picture including orthodox characteristics of a certain programming language in order to get a whole concept of the language?
\item What if we can expect hindrances that many people experienced before so that we can invest sufficient time to resolve issues rather than dropping out?
\item What if we can have shortcuts and bookmarks to answers to most problematic, cumbersome issues or questions while programming?
\item What if novices or experts can contribute to the other’s meta-learning process by drawing a big-picture letting them know what further steps are?
\end{enumerate}

\subsection{Design tenets}

\begin{itemize}
\item a programmer should quickly have access to previous explorations he has done. We do not want him to google the same concepts over and over again. Our tool should track the programmer’s learning progress so he can quickly revisit past concepts.
\item a programmer should not be assaulted with so much information that it becomes meaningless to him. He should receive suggestions that are most pertinent for the language topic he is currently exploring. Moreover, he should be able to refine, keep and collate only the suggestions he finds useful.
\item a programmer should be able to search and refine. He should be able to search different sources for hints, theory and practical explanation for different language concepts (SO, delicious etc). He should then be able to refine and retrieve concrete and diverse code examples that detail the particular topic (GitHub, SF etc)
\item a programmer should also receive help for the particular context he is coding in. The tool should be able to retrieve patterns of the code under edit and retrieve previously explored topics that deal with that code. Thus, the programmer can have the option to tailor searching and refining for the code under edit.
\end{itemize}

\section{Preliminary work}
\label{sec:prelim-work}

Many visualization system have been developed over the past years to help people learning programming language. By using computer graphics, workflow chart, and animation to help illustrate and present computer programs, processes, and algorithms.

\subsection{Jeliot 3 \cite{moreno2004visualizing}}

Jeliot 3 is a Program Visualization application. It visualizes how a Java program is interpreted. Method calls, variables, operation are displayed on a screen as the animation goes on, allowing the student to follow step by step the execution of a program. Programs can be created from scratch or they can be modifyed from previously stored code examples. The Java program being animated does not need any kind of additional calls, all the visualization is automatically generated. Jeliot 3 understands most of the Java constructs and it is able to animate them. Especial effort is currenlty being addressed to animate object oriented features, such as inheritance.

\begin{figure}[h!tb]
	\includegraphics[width=\textwidth]{jeliot3.png}
\caption{Jeliot program interface}
\label{fig:jeliot3}
\end{figure}

Much research has been conducted on how people learn to program, and many techniques have been proposed.It seems that there are two approaches \cite{mayer1981psychology} which can deeply enhance learning: concrete models and personal models.

It has been shown that people who are presented with a concrete, simple model of the larger concept they are about to learn can gain a quicker understanding and retain much more than people who are deprived of such a model.

It has also been shown that people who are encouraged to make their own personal model of the concept they are learning, “putting things in one’s words”,  gain a much deeper understanding than people who do not undertake such activities.

By drawing insight from the above concepts, we present a tool that aids the programmer in learning, understanding, exploring and recalling a new programming language. On one hand the tool can present the hot topics of a particular programming language, as mined from the collective knowledge of online platforms such as Stack Overflow, Delicious or Github. On the other hand it allows the programmer to construct a unique mental model that represents that programmer’s unique learning journey.

\subsection{Tool description}

Enable the programmer to build a personalized map, similar in form to the below examples,, that tracks his learning progress through a new language or concept. The programmer uses this map to search for and refine new knowledge and to keep track of all the concepts and related documents so far.

Advanced programmers can use this map as a continuous syntax reminder, instead of googling the same examples over and over again. The novice programmer can also use this map to document more theoretical knowledge such as basic algorithms and code idioms (eg: how to filter or aggregate collections by using loops).

Thus we can see two main functions of this map: to store knowledge in a structured form and to search for similar or new knowledge.

In terms of \emph{storing knowledge}, each node in the map would contain several documents. These are tutorials, forum questions and code snippets that helped the programmer in the past. In this manner, he does not have to spend time looking for the same examples over and over again.

Another important concept in terms of storing knowledge is that the map retains only what the programmer finds useful, only what he wants to keep for later reference. How does a programmer know whether to persist or not? Usually he does not know initially what is important (problem addressed below). This knowledge comes when he finds himself searching for the same concept more than once. Of course, this manner of growing the map is unique to every person.

In terms of \emph{searching for similar or new knowledge}, there would be two main approaches to grow the map: searching online places such Stack Overflow, Delicious or Github and suggestions based on similar maps from other users.

When searching online, the map tries to find similar hot topics related to the current context: For example, let’s say that the current map selection is Python \rarrow{} Sets. The map could then suggest hot topics related to Python sets by searching popular tags on Delicious or SO. It could find examples for set operations or set traversals. Python \rarrow{} Lists \rarrow{} Traversal would hopefully show different ways to traverse a list.

The map could also make suggestions of new map relations, nodes and documentation based on similar maps from other users.

In the end, we would also like to take this map into the IDE and let it suggest help according to the context under edit. While coding, the programmer could ask help about the current context. The map could either find the required knowledge in its structure (it has been previously searched by the programmer) or it could search help platforms and code repositories for questions, tutorials and code snippets most similar to code under edit.

\subsection{Steps}

Since this is a big project, we shall implement it in steps, as detailed below.

\subsubsection{Programming language map}

\textbf{High probability to be finished during course project}

Code search have always been essential to software development; it is the cornerstone of activities such as program comprehension and maintenance. In this step, we will introduce learn-by-code and learn-by-questions technologies.

The first stage would be to build the map of hot topics concerning a particular programming language. We shall use Stack Overflow and Delicious to find these hot topics. In this manner we use the accumulated knowledge of the crowd to find what is important and difficult for that particular language.

Both platforms have web services through which we can retrieve popular tags.

To guide the search we need a seed of important concepts that detail the main elements of programming languages (ex: statement, decision, iteration, function, class, inheritance etc). To find these seeds we shall review literature involving learning  programming languages. We shall also conduct interviews with both novice and experienced programmers.

These seed concepts will act as a scaffold on which our map is built. We will use them to bootstrap the web platform search.

Programming language map will function like a cheat sheet which will dynamically change based on your code snippets. All these information in the map will not be visible to the developers during coding process. When the developer introduces some concepts into the code, the related nodes will be shown up in our map. For instance, if the developer did not extend any class, he will not see information and code snippets related with inheritance.

In overall, the map will have 2 different modes. First mode enables developers to introduce new concepts (e.g., array iteration, inheritance) with simple code snippets. These code snippets will come from our previously mined repositories \cite{okur2012developers}. Second mode will enable developers to explore advanced topics through our information map mined from Stack Overflow and Delicious.

\subsubsection{Customize the map}
\textbf{Medium probability to be finished during course project.}

The above maps are centered around a particular programming language. They are not unique or personalized to the user.

In this phase we would like to let the user customize the map. He should be able to add or delete nodes that he is not interested in. He should also be able to edit nodes by deleting and adding documentation of his own (notes, code snippets, urls, tutorials etc)

The map should be able to reconstruct itself it by populating the nodes added by the user.

\subsubsection{Map mimics the learning progress}
\textbf{Medium to low probability to be finished during course project.}

The map should grow with the user. He could start with a single node, let’s say ``Python''. He should get suggestions according to the concept seeds in order to guide him, if he wishes so.

He should be able to add new nodes of his own accord and retrieve information and documentation specific for that particular node in the map.

\subsubsection{Plug into IDE}
\textbf{Low probability to be finished during course project.}

The map can live inside the IDE to offers help according to the code context under edit.

\subsection{A feel of what should be}

Three design prototypes are presented in figures \ref{fig:map1}, \ref{fig:map2} and \ref{fig:map3}.

\begin{figure}[hbt]
	\includegraphics[width=\textwidth]{map1.png}
\caption{Design protype 1}
\label{fig:map1}
\end{figure}

\begin{figure}[hbt]
	\includegraphics[width=\textwidth]{map2.png}
\caption{Design protype 2}
\label{fig:map2}
\end{figure}

\begin{figure}[hbt]
	\includegraphics[width=\textwidth]{map3.png}
\caption{Design protype 3}
\label{fig:map3}
\end{figure}

\clearpage

\section{Methods}

Mostly will use the well-known and effect design methods such as
\begin{itemize}
\item \hyperref[1]{http://socialinnovation.typepad.com/silk/silk-method-deck.html}
\item \hyperref[2]http://www.ideo.com/work/method-cards
\end{itemize}

\section{Time schedule}

\begin{table}[hbt]
\begin{tabular}{| l |p{6.5cm} | p{5cm} |}
\hline
\textbf{Date} & \textbf{Tasks} & \textbf{Deliverables} \\
\hline \hline
February 28 & Consult with Professor Bailey. Report to IRB. & Proposal revision \\ \hline
March 5 & W1: Interview(Consult) with Experts & Interview Report \\ \hline
March 7 & W2: Field Research & Insight Report \\ \hline
March 12 & W3: User Research & Insight Report \\ \hline
March 14 & W4: Concept Design: Goals, Persona and Ideation & Paper Prototype \\ \hline
March 19 & SPRING BREAK & - \\ \hline
March 21 & SPRING BREAK & - \\ \hline
March 26 & W5: Prototyping and Iteration 2; Consult with Prof. Bailey & Storyboard(Wireframe)
or \newline Working prototype \\ \hline
March 28 & W6: Self reflection & Project progress report \\ \hline
April 2 & W7: Implementation and Iteration 1 & UI design \\ \hline
April 4 & W8: Implementation and Iteration 2, Crowdsourcing 1 & Sourcecode, HIT results \\ \hline
April 9 & W9: Implementation and Iteration 3, Crowdsourcing 2 & Sourcecode, HIT results \\ \hline
April 11 & W10: Usability Test, Post User Interview & Experiment report \\ \hline
April 16 & W11: Statistical analysis and Discussion & Analysis Report \\ \hline
April 18 & W12: Write the final paper	 & Final paper draft \\ \hline
April 23 & Project presentations, Peer-review and revise 1 & Final paper revision 1 \\ \hline
April 25 & Project presentations, Peer-review and revise 2 & Final paper revision 2  \\ \hline
May 1 & Final Paper due & Final paper submit \\ \hline
\end{tabular}
\end{table}

\clearpage

\nocite{brand2005information}
\nocite{deek1999common}
\nocite{lahtinen2005study}
\nocite{lazonder2008information}
\nocite{murphy2006women}
\nocite{fincher1999we}
\nocite{pane1996usability}
\nocite{robins2003learning}
\nocite{soloway1989studying}
\nocite{winslow1996programming}
\nocite{mayer1981psychology}
\nocite{okur2012developers}

\bibliographystyle{plain}
\bibliography{proposal.bib}

\end{document}

### 2013-04-29 paper/paper.tex
initial paper commit

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\title{Croder Bringing the knowledge of the crowds into the IDE}
\author{Mihai Codoban \and Caius Brindescu \and Semih Okur \and Kyungho Lee \and Shuo Yuan}

\begin{document}
\section{Introduction}
\section{Why integrate reviews into the IDE}
\section{Related work}
\section{Selecting code snippets}
\section{Stackexchange code review characteristics}
\section{Interface with StackExchange}
\section{Review management in the IDE}
\section{Crowd sourced peer review creation}
\section{Tying review outcomes to the code}
\section{Preliminary user study}
\section{Sketches}
\section{Evaluation}
\section{Conclusion}
\end{document}

### 2013-04-29 paper/paper.tex

@@
 \usepackage{amssymb}
-\title{Croder Bringing the knowledge of the crowds into the IDE}
-\author{Mihai Codoban \and Caius Brindescu \and Semih Okur \and Kyungho Lee \and Shuo Yuan}
+
+\title{Croder \\ Bringing the Knowledge of the Crowds into the IDE}
+\author{Semih Okur \and Mihai Codoban \and Caius Brindescu \and Kyungho Lee \and Shuo Yuan}
 
 \begin{document}
+
+\maketitle
+
 \section{Introduction}
@@
 \section{Conclusion}
+
 \end{document}

### 2013-05-02 paper/paper.tex
Format to SIGCHI standard.

@@
-\documentclass[10pt,letterpaper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
+\documentclass[]{sigchi}
+
+% Arabic page numbers for submission. 
+% Remove this line to eliminate page numbers for the camera ready copy
+\pagenumbering{arabic}
+
+% Load basic packages
+\usepackage{balance}  % to better equalize the last page
+\usepackage{graphics} % for EPS, load graphicx instead
+\usepackage{times}    % comment if you want LaTeX's default font
+\usepackage{url}      % llt: nicely formatted URLs
+
+% llt: Define a global style for URLs, rather that the default one
+\makeatletter
+\def\url@leostyle{%
+  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
+\makeatother
+\urlstyle{leo}
+
+% To make various LaTeX processors do the right thing with page size.
+\def\pprw{8.5in}
+\def\pprh{11in}
+\special{papersize=\pprw,\pprh}
+\setlength{\paperwidth}{\pprw}
+\setlength{\paperheight}{\pprh}
+\setlength{\pdfpagewidth}{\pprw}
+\setlength{\pdfpageheight}{\pprh}
+
+% Make sure hyperref comes last of your loaded packages, 
+% to give it a fighting chance of not being over-written, 
+% since its job is to redefine many LaTeX commands.
+\usepackage[pdftex]{hyperref}
+\hypersetup{
+pdftitle={SIGCHI Conference Proceedings Format},
+pdfauthor={LaTeX},
+pdfkeywords={SIGCHI, proceedings, archival format},
+bookmarksnumbered,
+pdfstartview={FitH},
+colorlinks,
+citecolor=black,
+filecolor=black,
+linkcolor=black,
+urlcolor=black,
+breaklinks=true,
+}
+
+% create a shortcut to typeset table headings
+\newcommand\tabhead[1]{\small\textbf{#1}}
 
@@
 \author{Semih Okur \and Mihai Codoban \and Caius Brindescu \and Kyungho Lee \and Shuo Yuan}
+\numberofauthors{5}
+\author{
+  \alignauthor Semih Okur\\
+    \affaddr{University of Illinois at Urbana-Champaign}\\
+    \affaddr{Urbana, IL}\\
+    \email{okur2@illinois.edu}
+  \alignauthor Mihai Codoban\\
+    \affaddr{University of Illinois at Urbana-Champaign}\\
+    \affaddr{Urbana, IL}\\
+    \email{codo@illinois.edu}
+  \alignauthor Caius Brindescu\\
+    \affaddr{University of Illinois at Urbana-Champaign}\\
+    \affaddr{Urbana, IL}\\
+    \email{brind@illinois.edu}
+   \alignauthor Kyungho Lee\\
+    \affaddr{University of Illinois at Urbana-Champaign}\\
+    \affaddr{Urbana, IL}\\
+    \email{klee141@illinois.edu}
+  \alignauthor Shuo Yuan\\
+    \affaddr{University of Illinois at Urbana-Champaign}\\
+    \affaddr{Urbana, IL}\\
+    \email{syuan20@illinois.edu}
+}
 

### 2013-05-03 paper/paper.tex
Removed evaluation
Added text about general crowd sourcing
This is for issue #24

@@
 \section{Selecting code snippets}
+
+\section{Crowds for software development}
+
+One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
+first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
+qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
+We needed to aim for a platform where we were guaranteed to have the right audience.
+
+Mechanical Turk tasks tend to be very simple and require only minimal knowledge and cognitive
+skills. During one experiment we asked a technical question about JavaScript. Out of the 10 hits,
+9 were complete in 7 days. This partly shows that the Mechanical Turk platform is ill-suited for tasks
+that require a lot of specialized knowledge.
+
+Services such as eLance\footnote{\url{http://www.elance.com}} and oDesk\footnote{\url{http://www.odesk.com}}
+employ a crowd to complete programming tasks. But unlike typical crowd sourcing platforms, is it
+an offer based system. The requester posts the description for a task and workers bid to complete it.
+The requester then chooses a winner and then work on the project can start. This system is not what
+we are looking for. We needed a system where you can post your task and workers would select the
+task and complete it for a predetermined amount.
+
 \section{Stackexchange code review characteristics}
@@
 \section{Sketches}
-\section{Evaluation}
 \section{Conclusion}

### 2013-05-03 paper/paper.tex
Added bibliography
A small database with only 4 references.
Added more info to the general CrowdSourcing section
Again, this is for issue #24

@@
-\documentclass[]{sigchi}
+\documentclass{sigchi}
 
@@
 skills. During one experiment we asked a technical question about JavaScript. Out of the 10 hits,
-9 were complete in 7 days. This partly shows that the Mechanical Turk platform is ill-suited for tasks
-that require a lot of specialized knowledge.
+9 were complete in 7 days. Of those 9 tasks, only 4 useful and most of them were incomplete. This partly 
+shows that the Mechanical Turk platform is ill-suited for tasks that require specialized knowledge.
 
@@
 task and complete it for a predetermined amount.
+
+StackOverflow\footnote{\url{http://www.stackoverflow.com}} allow uses to post questions and get
+answers. The service is larger than most social Q\&A and technical forums. With a median answer time 
+of 11 minutes and a very active user user base \cite{Mamykina2011} it makes a good candidate for a
+platform to run the experiment. StackOverflow is part of a network of sites (StackExchange\footnote{\url{http://www.stackexchange.com}} that follow the same modes. One of them, \emph{Code
+Review Stack Exchange}\footnote{\url{http://codereview.stackexchange.com}} is based around the
+concept of concept of code review. It is this platform that we have used to test our protype.
 
@@
 
+\bibliographystyle{acm-sigchi}
+\bibliography{paper}
+
 \end{document}

### 2013-05-03 paper/paper.tex
Added a picture of the wizard
Issue #9
Added text for the wizard part
Again, for issue #9

@@
 \section{Review management in the IDE}
+
 \section{Crowd sourced peer review creation}
+
+For creating of the task we chose to implement a wizard. One of the main features is that you can ask
+for \emph{structured} code review. The user can select a criteria under which code review should be
+performed (performance, design, readability etc.). This helps reviews in keeping a focus on a given task.
+Also, to make it easier for them to understand the code, we allow the users to add a small note regarding
+the purpose and content of each code snippet. The code snippets are selected directly from the IDE.
+
+In figure~\ref{fig:wizard} we show the design approach we took. While it is a bit crude, it does offer all
+the features and presents the structured approach to creating the task. It is worth mentioning that the user
+has the option to add a general comment at an earlier stage in the wizard.
+
+\begin{figure}[hbt]
+	\includegraphics[width=\columnwidth]{wizard.png}
+\caption{Adding comments for each snippet}
+\label{fig:wizard}
+\end{figure}
+
 \section{Tying review outcomes to the code}

### 2013-05-03 paper/paper.tex
More text
Issue #9
Moved the figure.
You can't see it yet in the result, but as more text is added it should
fall into the propper place.
Added content and a figure for the markers
This addresses issue #10

@@
 
+After entering all the details needed for a task, the user can then select the service to post it to. For the
+moment we only offer integration with StackExchange, but other services can be added as well (like
+oDesk, eLance etc).
+
 \section{Tying review outcomes to the code}
+
+Once you submit the code, it can be difficult to remember what task relates to what code. In order to help
+the programmer we decided to mark code snippets that were sent off for review. The icon on the right
+rules notifies the developer if any replies have been received.
+
+\begin{figure}[hbt]
+	\includegraphics[width=\columnwidth]{marker.png}
+\caption{The market that corresponds to the review}
+\label{fig:marker}
+\end{figure}
+
+Figure~\ref{fig:marker} presents this concept. The code marked by the red box has been submitted of
+review. Clicking on the marker will bring up the review task associated with it.
+
 \section{Preliminary user study}

### 2013-05-03 paper/paper.tex
added code snippet chapter

@@
 
-\title{Croder \\ Bringing the Knowledge of the Crowds into the IDE}
+\newcommand{\croder}{\textbf{Croder }}
+\newcommand{\IDE}{\textbf{IDE }}
+\newcommand{\eclipse}{\textbf{Eclipse }}
+
+\title{Croder: Bringing the Knowledge of the Crowds into the IDE}
 \author{Semih Okur \and Mihai Codoban \and Caius Brindescu \and Kyungho Lee \and Shuo Yuan}
@@
 \section{Related work}
-\section{Selecting code snippets}
 
 \section{Crowds for software development}
-
 One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
@@
 \section{Interface with StackExchange}
+
+\section{Selecting code snippets}
+
+ The first step that the programmer must undergo when composing a code review is of course choosing the code snippets that she desires to be reviewed.
+The programmer must be able to compose several code snippets that together paint an overall picture of the concept they want to portray.
+For example snippets could range from lines of code, to loops, to whole classes and packages.
+
+ \croder allows the programmer to easily choose snippets from many places in the \IDE.
+The reasoning behind this is that if a resource contains or points to code, \croder should be able to transform it into a snippet.
+Figure \ref{fig:snippetSelection} shows  various resources which \croder can convert to code snippets, such as random editor selections, fields, methods and whole classes.
+As can be seen, resources originate from diverse views.
+
+ In order to track what snippets have been added to the review so far, a view is provided that holds each snippet. Figure \ref{fig:snippetViewer} illustrates this concept.
+
+ With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
+Section \ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.
+
 \section{Review management in the IDE}

### 2013-05-03 paper/paper.tex
added screenshots
moved section down
added future work
added review management section

@@
 
+ %TODO fix section reference
  With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
-Section \ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.
+Section~\ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.
 
-\section{Review management in the IDE}
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[scale=0.4]{snippetSelections.png}
+\caption{Adding code snippets from various resources}
+\label{fig:snippetSelection}
+\end{figure}
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[scale=0.45]{snippetViewer.png}
+\caption{Viewing code snippets}
+\label{fig:snippetViewer}
+\end{figure}
+
+\begin{figure}[hbt]
+	\includegraphics[width=\columnwidth]{wizard.png}
+\caption{Adding comments for each snippet}
+\label{fig:wizard}
+\end{figure}
 
@@
 
+\section{Review management in the IDE}
+
+In time, the programmer creates many reviews as she seeks to improve herself and her code. She may also wish to keep certain reviews for future reference.
+
+\croder keeps track of current and past reviews.
+Moreover, for each review it fetches the associated replies.
+Figure~\ref{fig:reviewBrowser} illustrates the Review Browser.
+The left pane shows the review titles while the right pane shows the replies for the currently selected review.
+
+%TODO fix section reference
+Section~\ref{sec:future} illustrates several features which can enhance the tool's capabilities via review management.
+
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[scale=0.3]{reviewBrowser.png}
+\caption{Viewing code snippets}
+\label{fig:snippetViewer}
+\end{figure}
+
 \section{Preliminary user study}
 \section{Sketches}
+
+\section{Future Work}
+\label{sec:future}
+
+%expand bullets from presentation slides
+%snippet selector
+%review browser: respond, migrate to other browsers
+
 \section{Conclusion}

### 2013-05-03 paper/paper.tex
added new section
added chapter about Software development for crowds

@@
 \section{Related work}
+
+\section{Software development for crowds}
+
+The main research theme that was explored throughout this project is whether software development is suitable for the crowds.
+\textit{Are there any software development micro-tasks which can be successfully accomplished in reasonably short time by the crowds?}
+
+These tasks would need to take into consideration the main issue with crowdsourced tasks, that is, the lack of context.
+By the very nature of these short lived tasks workers cannot know the scope of the entire project.
+This poses severe limitations on task size since they have to be complete enough to offer the minimum amount of context for the work to be tractable, but must not be so large as to exceed the definition of micro-tasks.
+Deviations in any of the two conflicting constraints would make the task unattractive to workers.
+
+We identified three activities that have a high chance of being crowdsourced.
+
+\textbf{Code reviews}.
+In a usual code review, the author of the code selects a list of code snippets that he wants reviewed and then sends them to a list of reviewers.
+Reviewers usually consist of people working on the same project, since they have the most knowledge about the system particularities.
+They spend time going through the code both in isolation and together in a meeting.
+A list of issues is compiled at the end of the meeting.
+The usual outcomes of a code review are defect detection, design and code improvement, alternative solutions and dissemination of knowledge inside the team.
+
+Therefore code reviews seem to represent a natural choice for crowdsourcing since they are usually performed by a team of people and the outcome represents the accumulated knowledge of these individuals.
+However, in terms of review outcomes, crowdsourced code reviews would provide value only to those outcomes that do not require great context.
+This means that tasks such as defect detection, high level design improvements and general issues that deal with the mapping of requirements to code would not pose good candidates.
+
+On the other hand, crowds could be used to catch trivial and beginner mistakes.
+By deferring these issues, more value can be obtained from inside code reviews.
+Project colleagues would not waste time on these simple issues any more and could better dedicate their time and knowledge to finding high level issues that involve knowledge of the problem domain and implementation history.
+
+\textbf{Tests}.
+The crowd could be asked to write tests for different software entities such as methods or classes.
+Such a task could prove suitable since there are standardized, almost mechanical procedures to writing tests.
+For methods, the crowd could provide black box tests, by making use of the method contract, or white box tests, by making use of the method's control and data flow.
+For classes, the crowd would create a composition of method tests together with class contract tests.
+
+However, there are drawbacks and limitations to this kind of task.
+Tests would require some documentation of method and class contracts.
+The code under test may have dependencies that require to be stubbed away.
+High level requirement validation tests cannot be produced due to lack of context.
+
+\textbf{Code transformations on request}.
+There are a series of tedious program transformations, both refactorings and behaviour changing transformations that are tedious enough to warrant automation but require too much domain knowledge to warrant automation.
+On one hand, developer time would be wasted on these mechanical tasks.
+On the other hand, the effort required to automatize them makes it intractable to apply to many, short lived transformations.
+
+Examples on the refactoring side could be loop transformations for parallel execution, task boundary identification for parallel execution, code rewriting for better readability, etc.
+On the behaviour changing side, we can remind transformations such as introducing the visitor pattern to a large hierarchy or changing the code from using a certain library to another.
+
+There are of course drawbacks and difficulties with this approach.
+Some tasks could require much more context information than the requester anticipated.
+The requester will have to inspect all proposed code changes which would annihilate part of the advantage of deferring work to somebody else.
+
+From these three candidates for software development micro-tasks we chose to dedicate our efforts on providing support for code reviews.
+This seems like a natural starting point due to its social characteristics.
+From the three potential tasks, code reviews require the least amount of specialized, focused knowledge which should make them attractive to a wider audience and could potentially be of most value to the programmer.
+The latter justification pertains to the fact that tests and code transformations are of modest educational value to the programmer while code reviews aid in self improvement.
 

### 2013-05-03 paper/paper.tex
added future work

@@
 \section{Crowds for software development}
+\label{sec:crowds}
 One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
@@
 	\centering
-	\includegraphics[scale=0.3]{reviewBrowser.png}
+	\includegraphics[scale=0.4]{reviewBrowser.png}
 \caption{Viewing code snippets}
@@
 \label{sec:future}
+
+Future work can be done in several directions.
+
+The only platform currently used by \croder is Stackexchange code review due to reasons such as familiarity with the platform, constant activity and most importantly, it represents a crowd that is accustomed to the code review task type.
+Future work in this regard would see \croder gain adapters for other platforms such as eLance or oDesk.
+On one hand, these platforms have mature APIs and sandboxed testing environments.
+On the other hand their crowds are not accustomed to micro-tasks.
+
+%TODO fix section reference
+Indeed, as was stated in section~\ref{sec:crowds}, eLance and oDesk crowds perform software outsourcing.
+Their tasks range from days to months and the compensation from tens to thousands of dollars.
+If we are to utilize these crowds then we shall have to experiment and see if we can get them accustomed to the micro-tasks of crowdsourcing.
+This implies that we will have to effectively teach the crowd.
+We shall have to start with oversized tasks and progressively decrease them in size and scope.
+We shall have to experiment with task size and compensation amount in order to find the sweet spots.
+
+Automatic evaluation of crowdsourced reviews is also problematic.
+One cannot simply generate random code snippets of different size and complexity.
+Code snippets have to have a coherent story behind them otherwise the required specialized workers will not engage in their review.
+
+Relating to code snippets, \croder currently leaves code snippet selection solely in the hands of the programmer.
+Unfortunately, while collecting the code to be reviewed, the programmer may miss essential snippets that complete the story of the review.
+We propose a semi automated approach in which \croder would suggest a least amount of additional snippets in order to have a more complete review.
+There are different solutions we can utilize in order to achieve this goal such as a metric based approach: a dependency and coupling analysis can be performed on the selected code snippets in order to find outside potential snippets that would minimize certain metrics.
+
+In terms of the current implementation, particular code reviews are tied to only one \IDE installation.
+The feature to share and access the review results with other colleague's \IDE's would be most welcome.
+
+Last but not least, code reviews represent only one possible software development task that can be crowdsourced.
+We identified several more, such as testing or on demand code transformations.
+In order to fully bring the knowledge of the crowds into the \IDE, \croder will have to learn how to crowdsource many more tasks, starting with the ones previously mentioned.
 

### 2013-05-03 paper/paper.tex
Fixed the references.
Also removed one duplicated figure.

@@
 \usepackage{url}      % llt: nicely formatted URLs
+\usepackage{nameref}
 
@@
 \label{sec:crowds}
+
 One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
@@
  With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
-Section~\ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.
+The \nameref{sec:future} section describes a technique which offers suggestions on other possible snippets based on the current ones.
 
@@
 \label{fig:snippetViewer}
-\end{figure}
-
-\begin{figure}[hbt]
-	\includegraphics[width=\columnwidth]{wizard.png}
-\caption{Adding comments for each snippet}
-\label{fig:wizard}
 \end{figure}
@@
 	\centering
-	\includegraphics[scale=0.4]{reviewBrowser.png}
+	\includegraphics[width=\columnwidth]{reviewBrowser.png}
 \caption{Viewing code snippets}
-\label{fig:snippetViewer}
+\label{fig:reviewBrowser}
 \end{figure}

### 2013-05-03 paper/paper.tex
Integrated the work done for sketches
Issue #19

@@
 \section{Preliminary user study}
+
 \section{Sketches}
+
+Based on user interview study, we start to draw some initial sketches of workflow. At the beginning of 
+drawing sketches, we focus on interface simplification. Many interviewee mentioned that it is a really 
+hard time at the beginning of learning code specially for designers, architects or other students --
+because they do not have any professional education background of computer science or coding. So 
+based on simplification principle, we hide many features on main menu, make it more user-friendly and 
+still have consistency and hierarchy between different features (see Figure~\ref{fig:sketches}).
+
+\begin{figure}[hbt]
+	\includegraphics[width=\columnwidth]{sketch1.jpg}
+	\includegraphics[width=\columnwidth]{sketch2.jpg}
+\caption{Initial design sketches}
+\label{fig:sketches}
+\end{figure}
+
+After Showing these initial sketches to our interviewees, we got feedback about layout and interface 
+graphic hierarchy. Based on these feedbacks, we developed a new interface for our program 
+(Figure~\ref{fig:new interface}). Using metaphor method, the interface is like a hand-made leather 
+cover notebook. This interface can recall user’s memory of using notebook to take note in class, in 
+the meantime, make first time user specially user without background of coding quickly familiar with 
+program.
+
+\begin{figure}[hbt]
+\begin{center}
+	\includegraphics[width=0.8\columnwidth]{newinterface1.jpg}
+	\includegraphics[width=0.8\columnwidth]{newinterface2.jpg}
+	\includegraphics[width=0.8\columnwidth]{newinterface3.jpg}
+	\includegraphics[width=0.8\columnwidth]{newinterface4.jpg}
+\end{center}
+\caption{Interface example}
+\label{fig:newinterface}
+\end{figure}
 

### 2013-05-03 paper/paper.tex
Fixed the commands
Made the figures 2x2
Added part of the motivation
Issue #15

@@
 
-\newcommand{\croder}{\textbf{Croder }}
-\newcommand{\IDE}{\textbf{IDE }}
-\newcommand{\eclipse}{\textbf{Eclipse }}
+\newcommand{\croder}{\textsc{Croder }}
+\newcommand{\IDE}{\emph{IDE }}
+\newcommand{\eclipse}{\emph{Eclipse }}
 
@@
 \section{Why integrate reviews into the IDE}
+
+Interruptions are bad because they break the flow of work and cause more stress \cite{Spolsky,Mark2008}. 
+Also, the interruptions that a developers faces are varied \cite{Czerwinski2004}, so trying to reduce that number
+will bring benefit to the workflow. By integrating the code review submission process into the \ide we can 
+reduce the time of the interruption. Also, because the developer never leaves the context of his work, we hope 
+that the effects of this interruption will be minimal.
+
+Integrating into the \ide has other benefits too. The \ide is the environment where the code lives. By taping into
+this resource we can get a lot more information about what the developer what to review. For example, suppose
+he wants to select a method for review. If that method is tightly couple with another one, than we can suggest that
+he include that method as well. Also, the developer never leaves the context. He can very easily go back to code
+to decide whether some snippet of code would be relevant or not to the reviewer.
+
+Another advantage is that we can submit discrete notification when a review has been received. This, again,
+reduces the distraction and makes it a lot easier to see what the review is about. By presenting the result of 
+the review in the \ide the developer can see it in context. This makes it a lot easier to come back in the context
+of the review and make sense of the comments.
+
 \section{Related work}
@@
 
-\begin{figure}[hbt]
+\begin{figure*}[hbt]
 \begin{center}
@@
 \label{fig:newinterface}
-\end{figure}
+\end{figure*}
 

### 2013-05-03 paper/paper.tex
Renamed the \ide command
Easier to type this way

@@
 \newcommand{\croder}{\textsc{Croder }}
-\newcommand{\IDE}{\emph{IDE }}
+\newcommand{\ide}{\emph{IDE }}
 \newcommand{\eclipse}{\emph{Eclipse }}
@@
 
- \croder allows the programmer to easily choose snippets from many places in the \IDE.
+ \croder allows the programmer to easily choose snippets from many places in the \ide.
 The reasoning behind this is that if a resource contains or points to code, \croder should be able to transform it into a snippet.
@@
 
-In terms of the current implementation, particular code reviews are tied to only one \IDE installation.
-The feature to share and access the review results with other colleague's \IDE's would be most welcome.
+In terms of the current implementation, particular code reviews are tied to only one \ide installation.
+The feature to share and access the review results with other colleague's \ide's would be most welcome.
 
@@
 We identified several more, such as testing or on demand code transformations.
-In order to fully bring the knowledge of the crowds into the \IDE, \croder will have to learn how to crowdsource many more tasks, starting with the ones previously mentioned.
+In order to fully bring the knowledge of the crowds into the \ide, \croder will have to learn how to crowdsource many more tasks, starting with the ones previously mentioned.
 

### 2013-05-03 paper/paper.tex
Added a reference to Brian's paper
Added the abstract

@@
 
+\begin{abstract}
+This paper presents a new way of doing code reviews. Since they take up a lot of time and require
+a great amount to coordination. We propose a new way doing reviews using the crowds. By 
+integrating the \ide{}'s with the review platform we hope to make it easier for developers to review
+code and have code reviews. To test our proposed solution, we have built a new tool, \croder{}, that
+can pot reviews and get results from StackExchange. This integration will help developers post
+tasks without the need of context switching.
+\end{abstract}
+
 \section{Introduction}
@@
 Interruptions are bad because they break the flow of work and cause more stress \cite{Spolsky,Mark2008}. 
-Also, the interruptions that a developers faces are varied \cite{Czerwinski2004}, so trying to reduce that number
-will bring benefit to the workflow. By integrating the code review submission process into the \ide we can 
-reduce the time of the interruption. Also, because the developer never leaves the context of his work, we hope 
-that the effects of this interruption will be minimal.
+Also, the interruptions that a developers faces are varied \cite{Czerwinski2004}, so a solution that reduces
+the number of interruptions is essential. \cite{Adamczyk2004}. By integrating the code review submission 
+process into the \ide we can  reduce the time of the interruption. Also, because the developer never leaves 
+the context of his work, we hope that the effects of this interruption will be minimal.
 

### 2013-05-03 paper/paper.tex
Command tweek are removed a useless line
Being a format nazi here
completed part of introduction

--- 2013-05-03 paper/paper.tex
@@
 \section{Introduction}
+
+Crowdsourced computing tasks have been sprouting everywhere lately, spanning over a diverse field of task types.
+They range from demographic studies (surveys), to personal inquiries (product preferences), to machine learning algorithm training (categorizing photos) and so on and so forth.
+One is limited only by imagination when customizing tasks for the crowd.
+
+This spike in crowdsourced work has been instigated by the rise of supporting platforms as well.
+Mechanical Turk\footnote{\url{https://www.mturk.com/mturk/}} has risen to be the \textit{de facto} crowdsourcing platform.
+The large worker base that this platform has enables a high degree of parallel task decomposition.
+Moreover, the same large worker base enables rapid task response times.
+By means of these two crucial characteristics crowdsourcing has become a viable means towards task execution and decomposition.
+
+An interesting application for crowdsourcing is in collaborative design.
+Workers with or without specialized knowledge participate to create something with a higher scope than the individual task.
+It falls to the requester's creativity to build tasks in such a way that by composing their results a bigger, holistic product is achieved.
+
+Starting from the previous observation and from related work as well we decided to explore the space of crowdsourced software development tasks.
+In this regard we cross-referenced the particularities of the crowd with the particularities of software development tasks in order to find suitable candidates.
+We produced three potential tasks that would be suitable for crowdsourcing: code reviews, test generation and semi-mechanical code transformations.
+
+For the scope of this paper we focused on code reviews for reasons detailed in the
+
+what if progr tasks. integrate with IDE
+
+specialize on code review
+
+tool
+
+benefit from stack exchange
+
+preliminary used study?
+
 \section{Why integrate reviews into the IDE}

### 2013-05-03 paper/paper.tex

@@
 
-\newcommand{\croder}{\textsc{Croder }}
+\newcommand{\croder}{\textsc{Croder}}
 \newcommand{\ide}{\emph{IDE }}
@@
 \maketitle
+
+\begin{abstract}
+This paper presents a new way of doing code reviews. Since they take up a lot of time and require
+a great amount to coordination. We propose a new way doing reviews using the crowds. By 
+integrating the \ide{}'s with the review platform we hope to make it easier for developers to review
+code and have code reviews. To test our proposed solution, we have built a new tool, \croder{}, that
+can pot reviews and get results from StackExchange. This integration will help developers post
+tasks without the need of context switching.
+\end{abstract}
 

### 2013-05-03 paper/paper.tex
Corrected small errors and omissions
Also rephrased bad phrasing and respelled bad spelling

--- 2013-05-03 paper/paper.tex
@@
 \usepackage{nameref}
+\usepackage{xspace}
 
@@
 
-\newcommand{\croder}{\textsc{Croder }}
-\newcommand{\ide}{\emph{IDE }}
-\newcommand{\eclipse}{\emph{Eclipse }}
+\newcommand{\croder}{\textsc{Croder\xspace}}
+\newcommand{\ide}{\emph{IDE\xspace}}
+\newcommand{\eclipse}{\emph{Eclipse\xspace}}
 
@@
 \begin{abstract}
-This paper presents a new way of doing code reviews. Since they take up a lot of time and require
-a great amount to coordination. We propose a new way doing reviews using the crowds. By 
-integrating the \ide{}'s with the review platform we hope to make it easier for developers to review
-code and have code reviews. To test our proposed solution, we have built a new tool, \croder{}, that
+This paper proposes a new way of doing code reviews. Since they take up a lot of time and require
+a great amount of coordination, we suggest using the crowds to fulfill this task. By 
+integrating the \ide with the review platform we hope to make it easier for developers to review
+code and have code reviews. To test our proposed solution, we have built a new tool, \croder, that
 can pot reviews and get results from StackExchange. This integration will help developers post
@@
 Interruptions are bad because they break the flow of work and cause more stress \cite{Spolsky,Mark2008}. 
-Also, the interruptions that a developers faces are varied \cite{Czerwinski2004}, so a solution that reduces
-the number of interruptions is essential. \cite{Adamczyk2004}. By integrating the code review submission 
-process into the \ide we can  reduce the time of the interruption. Also, because the developer never leaves 
+Also, the interruptions that a developers face are varied \cite{Czerwinski2004}, so a solution that reduces
+this number is essential. \cite{Adamczyk2004}. By integrating the code review submission 
+process into the \ide we can reduce the impact of the interruption. Also, because the developer never leaves 
 the context of his work, we hope that the effects of this interruption will be minimal.
@@
 this resource we can get a lot more information about what the developer what to review. For example, suppose
-he wants to select a method for review. If that method is tightly couple with another one, than we can suggest that
-he include that method as well. Also, the developer never leaves the context. He can very easily go back to code
+he wants to select a method for review. If that method is tightly coupled with another one, than we can suggest that
+he includes that method as well. Also, the developer never leaves the context. He can very easily go back to the code
 to decide whether some snippet of code would be relevant or not to the reviewer.
 
-Another advantage is that we can submit discrete notification when a review has been received. This, again,
+Another advantage is that we can use discrete notifications when a review has been received. This, again,
 reduces the distraction and makes it a lot easier to see what the review is about. By presenting the result of 
 the review in the \ide the developer can see it in context. This makes it a lot easier to come back in the context
-of the review and make sense of the comments.
+of the review and make sense of the comments. We are hoping that this will increase the developer's productivity.
 
@@
 The main research theme that was explored throughout this project is whether software development is suitable for the crowds.
-\textit{Are there any software development micro-tasks which can be successfully accomplished in reasonably short time by the crowds?}
+\textit{Are there any software development micro-tasks which can be successfully accomplished in reasonably short time by specialized crowds?}
 
@@
 
-We identified three activities that have a high chance of being crowdsourced.
+We have identified three activities that have a high chance of being crowdsourced.
 
 \textbf{Code reviews}.
-In a usual code review, the author of the code selects a list of code snippets that he wants reviewed and then sends them to a list of reviewers.
+In a usual code review, the author of the code selects a number of code snippets that he wants reviewed and then sends them to a list of reviewers.
 Reviewers usually consist of people working on the same project, since they have the most knowledge about the system particularities.
-They spend time going through the code both in isolation and together in a meeting.
+They spend time going through the code both separately and together, in a meeting.
 A list of issues is compiled at the end of the meeting.
@@
 By deferring these issues, more value can be obtained from inside code reviews.
-Project colleagues would not waste time on these simple issues any more and could better dedicate their time and knowledge to finding high level issues that involve knowledge of the problem domain and implementation history.
+Project colleagues would not waste time on these simple issues any more and could better dedicate their time and knowledge to finding high level issues that involve knowledge of the problem domain and implementation.
 
@@
 For methods, the crowd could provide black box tests, by making use of the method contract, or white box tests, by making use of the method's control and data flow.
-For classes, the crowd would create a composition of method tests together with class contract tests.
+For classes, the crowd would create a composition of methods that tests the class' interface.
 
@@
 On one hand, developer time would be wasted on these mechanical tasks.
-On the other hand, the effort required to automatize them makes it intractable to apply to many, short lived transformations.
+On the other, the effort required to automatize them makes it intractable to apply to many, short lived transformations.
 
-Examples on the refactoring side could be loop transformations for parallel execution, task boundary identification for parallel execution, code rewriting for better readability, etc.
-On the behaviour changing side, we can remind transformations such as introducing the visitor pattern to a large hierarchy or changing the code from using a certain library to another.
+Examples on the refactoring side could be loop transformations and task boundary identification for parallel execution, code rewriting for better readability, etc.
+On the behavior changing side, we can remind transformations such as introducing the visitor pattern to a large hierarchy or changing the code from using a certain library to another.
 
@@
 One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
-first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
-qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
+first options was the Amazon Mechanical Turk platform. The main problem with this platform is the lack of
+qualified workers. Code reviewing is a very technical process that requires a large amount of knowledge.
 We needed to aim for a platform where we were guaranteed to have the right audience.
@@
 skills. During one experiment we asked a technical question about JavaScript. Out of the 10 hits,
-9 were complete in 7 days. Of those 9 tasks, only 4 useful and most of them were incomplete. This partly 
+9 were completed in 7 days. Of those 9 tasks, only 4 were useful and most of them were incomplete. This partly 
 shows that the Mechanical Turk platform is ill-suited for tasks that require specialized knowledge.
@@
 
-StackOverflow\footnote{\url{http://www.stackoverflow.com}} allow uses to post questions and get
+StackOverflow\footnote{\url{http://www.stackoverflow.com}} allow users to post questions and get
 answers. The service is larger than most social Q\&A and technical forums. With a median answer time 
 of 11 minutes and a very active user user base \cite{Mamykina2011} it makes a good candidate for a
-platform to run the experiment. StackOverflow is part of a network of sites (StackExchange\footnote{\url{http://www.stackexchange.com}} that follow the same modes. One of them, \emph{Code
+platform to run the experiments. StackOverflow is part of a network of sites, (StackExchange\footnote{\url{http://www.stackexchange.com}} that follow the same modes. One of them, \emph{Code
 Review Stack Exchange}\footnote{\url{http://codereview.stackexchange.com}} is based around the
-concept of concept of code review. It is this platform that we have used to test our protype.
+concept of code review. It is this platform that we have used to test our prototype.
 
-\section{Stackexchange code review characteristics}
-\section{Interface with StackExchange}
+\section{Stack Exchange code review characteristics}
+\section{Interface with Stack Exchange}
 
@@
 
- The first step that the programmer must undergo when composing a code review is of course choosing the code snippets that she desires to be reviewed.
+ The first step that the programmer must undergo when composing a code review is, of course, choosing the code snippets that she desires to be reviewed.
 The programmer must be able to compose several code snippets that together paint an overall picture of the concept they want to portray.
@@
  %TODO fix section reference
- With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
+ With today's \croder, the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
 The \nameref{sec:future} section describes a technique which offers suggestions on other possible snippets based on the current ones.
@@
 For creating of the task we chose to implement a wizard. One of the main features is that you can ask
-for \emph{structured} code review. The user can select a criteria under which code review should be
-performed (performance, design, readability etc.). This helps reviews in keeping a focus on a given task.
+for a \emph{structured} code review. The user can select a criteria under which code review should be
+performed (performance, design, readability etc.). This helps reviewers in keeping a focus on a given task.
 Also, to make it easier for them to understand the code, we allow the users to add a small note regarding
@@
 
-%TODO fix section reference
-Section~\ref{sec:future} illustrates several features which can enhance the tool's capabilities via review management.
+Section~\nameref{sec:future} illustrates several features which can enhance the tool's capabilities via review management.
 
@@
 
-Based on user interview study, we start to draw some initial sketches of workflow. At the beginning of 
-drawing sketches, we focus on interface simplification. Many interviewee mentioned that it is a really 
-hard time at the beginning of learning code specially for designers, architects or other students --
-because they do not have any professional education background of computer science or coding. So 
-based on simplification principle, we hide many features on main menu, make it more user-friendly and 
-still have consistency and hierarchy between different features (see Figure~\ref{fig:sketches}).
+Based on user interview study, we started to draw some initial sketches of the workflow. At the beginning of 
+drawing the sketches, we focused simplifying the interface. Many interviewees mentioned that they have a really 
+hard time beginning to learn code.  This is especially true for designers, architects etc. --
+because they do not have any professional education background in computer science or programming. So,
+based on the simplification principle, we hide many features in main menu, make it more user-friendly and 
+still have consistency and a hierarchy between different features (see Figure~\ref{fig:sketches}).
 
@@
 
-After Showing these initial sketches to our interviewees, we got feedback about layout and interface 
+After showing these initial sketches to our interviewees, we got feedback about layout and interface 
 graphic hierarchy. Based on these feedbacks, we developed a new interface for our program 
-(Figure~\ref{fig:new interface}). Using metaphor method, the interface is like a hand-made leather 
-cover notebook. This interface can recall user’s memory of using notebook to take note in class, in 
-the meantime, make first time user specially user without background of coding quickly familiar with 
-program.
+(Figure~\ref{fig:newinterface}). Using the metaphor method, the interface is like a hand-made leather 
+cover notebook. This interface can recall the user’s memory of using notebook to take notes in class.
+This can make first time users, especially user without background in programming, to quickly become
+familiar with programming.
 
@@
 
-The only platform currently used by \croder is Stackexchange code review due to reasons such as familiarity with the platform, constant activity and most importantly, it represents a crowd that is accustomed to the code review task type.
+The only platform currently used by \croder is StackExchange Code Review due to reasons such as: familiarity with the platform, constant activity and most importantly, it represents a crowd that is accustomed to the code review task type.
 Future work in this regard would see \croder gain adapters for other platforms such as eLance or oDesk.
@@
 %TODO fix section reference
-Indeed, as was stated in section~\ref{sec:crowds}, eLance and oDesk crowds perform software outsourcing.
+Indeed, as it was stated in section~\nameref{sec:crowds}, eLance and oDesk crowds perform software outsourcing.
 Their tasks range from days to months and the compensation from tens to thousands of dollars.
-If we are to utilize these crowds then we shall have to experiment and see if we can get them accustomed to the micro-tasks of crowdsourcing.
+If we are to utilize these crowds then we shall have to experiment and see if we can get them accustomed to the crowdsourcing micro-tasks.
 This implies that we will have to effectively teach the crowd.

### 2013-05-03 paper/paper.tex
did the introduction

--- 2013-05-03 paper/paper.tex
@@
 
-\newcommand{\croder}{\textsc{Croder}}
+\newcommand{\croder}{\textsc{Croder }}
 \newcommand{\ide}{\emph{IDE }}
@@
 
-For the scope of this paper we focused on code reviews for reasons detailed in the
+For the scope of this paper we choosed to focus on code reviews for reasons detailed in section~\nameref{sec:softcrowd}.
+In this regard we built a tool, \croder, which integrates with \eclipse to provide crowdsourced code reviews directly in the \ide.
+With \croder, programmers can build and run the whole process of code reviews directly from the \ide, from selecting code snippets, to posting the review to the crowd, to managing and accessing review outcomes.
 
-what if progr tasks. integrate with IDE
+In terms of crowd platforms we could not use Mechanical Turk because of the lack of specialized crowds.
+Instead, we analysed potential replacements like eLance, oDesc and Stackexchange.
+For reasons further in the paper we chose Stackexchange as the backend of \croder.
 
-specialize on code review
-
-tool
-
-benefit from stack exchange
-
-preliminary used study?
+To evaluate the need for \croder we conducted a study to assess potential user traits and to assess programmer's knowledge of crowdsourcing and code reviews.
+By means of this study we were then able to build three potential user personas and intuitive UI sketches.
 
@@
 \section{Software development for crowds}
+\label{sec:softcrowd}
 

### 2013-05-03 paper/paper.tex
Added the table from Lee

--- 2013-05-03 paper/paper.tex
@@
 
+\begin{table*}
+	\begin{center}
+	\begin{tabular}{| p{3cm} || p{4cm} | p{4cm} | p{4cm} |}
+	\hline
+	& Primary User & Secondary User & Tertiary User \\ \hline \hline
+	\textbf{Pseudoname} & Ben & Kyle & Karla \\ \hline
+	\textbf{Education} & PhD Student & MFA Graduate & MBA Student \\ \hline
+	\textbf{Type} & Pragmatic & Opportunistic & Exploratory \\ \hline
+	\textbf{Attitude} & Writes code methodically. Develops sufficient understanding of a technology
+		to enable component use of it. Prides himself or herself to building robust application or
+		technical challenges. & 
+		Writes code in an exploratory fashion. Develops a fundamental
+		understanding of a technology to understand how it can solve a specific problem &
+		Barely write code all by herself. Develop with limited understanding of Java language 
+		and she is having a trouble with developing her ideas with a basic syntax quite occasionally. \\ \hline
+	\textbf{Motto} & I want to focus on creating something new while somebody cleans up my slight mistakes. &
+		I sometimes feel dizzy because I can't find what is wrong with my code. &
+		I barely started to write code in Java to prove my model in the class. But I don't know how to. \\ \hline
+	\textbf{Computer literacy} & Expert. Majored in CS & Intermediate. Majored in Art and Design & Basic
+		Majored in Business \\ \hline
+	\textbf{Pair programming experience} & Java, C, C++, Matlab etc. & Adobe ActionScript, HTML/CSS,
+		Proce55ing, Java & Visual Basic, Mathematica \\ \hline
+	\textbf{Three Most frequent sites they use when they are programming} & GitHub, StackOverflow, Codeguru &
+		Google, StackOverflow, Open Processing & Google, eHow, Quora \\ \hline
+	\textbf{Goal} & Find related info; Find an optimized process or algorithm & Find related info; Find previous
+		Q\&A that may help his problem & Find source code; Looking for someone who can answer her
+		questions. \\ \hline
+	\end{tabular}
+	\end{center}
+\caption{Persona table to show their situation, background and goal to code review}
+\label{table:persona}
+\end{table*}
+
 \section{Sketches}

### 2013-05-03 paper/paper.tex
added phrase about persistency

--- 2013-05-03 paper/paper.tex
@@
 
- %TODO fix section reference
 With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
@@
 
-%TODO fix section reference
-Section~\ref{sec:future} illustrates several features which can enhance the tool's capabilities via review management.
+Since the code review results may take several days to arrive, and since the programmer may wish to keep certain reviews for future reference, \croder constantly persists review related artefacts such as snippets, code markers and review replies.
+Moreover, the persisted files can be moved from one \ide installation to another.
+
+Section~\nameref{sec:future} illustrates several features which can enhance the tool's capabilities via review management.
 
@@
 
-%TODO fix section reference
-Indeed, as was stated in section~\ref{sec:crowds}, eLance and oDesk crowds perform software outsourcing.
+Indeed, as was stated in section~\nameref{sec:crowds}, eLance and oDesk crowds perform software outsourcing.
 Their tasks range from days to months and the compensation from tens to thousands of dollars.

### 2013-05-03 paper/paper.tex
Made the table nicer

--- 2013-05-03 paper/paper.tex
@@
 \usepackage{xspace}
+\usepackage{array}
 
@@
 
-\begin{table*}
+\begin{table*}[hbt]
 	\begin{center}
-	\begin{tabular}{| p{3cm} || p{4cm} | p{4cm} | p{4cm} |}
+	\begin{tabular}{| m{3cm} || p{4cm} | p{4cm} | p{4cm} |}
 	\hline
-	& Primary User & Secondary User & Tertiary User \\ \hline \hline
+	& \begin{center}Primary User\end{center} & 
+		\begin{center}Secondary User\end{center} & 
+		\begin{center}Tertiary User\end{center} \\ \hline \hline
 	\textbf{Pseudoname} & Ben & Kyle & Karla \\ \hline
@@
 		Proce55ing, Java & Visual Basic, Mathematica \\ \hline
-	\textbf{Three Most frequent sites they use when they are programming} & GitHub, StackOverflow, Codeguru &
+	\textbf{Three most frequent sites they use when they are programming} & GitHub, StackOverflow, Codeguru &
 		Google, StackOverflow, Open Processing & Google, eHow, Quora \\ \hline

### 2013-05-03 paper/paper.tex

@@
 
- %TODO fix section reference
- With today's \croder, the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
+With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer.
 The \nameref{sec:future} section describes a technique which offers suggestions on other possible snippets based on the current ones.
@@
 The left pane shows the review titles while the right pane shows the replies for the currently selected review.
+
+Since the code review results may take several days to arrive, and since the programmer may wish to keep certain reviews for future reference, \croder constantly persists review related artefacts such as snippets, code markers and review replies.
+Moreover, the persisted files can be moved from one \ide installation to another.
 
@@
 
-%TODO fix section reference
-Indeed, as it was stated in section~\nameref{sec:crowds}, eLance and oDesk crowds perform software outsourcing.
+Indeed, as was stated in section~\nameref{sec:crowds}, eLance and oDesk crowds perform software outsourcing.
 Their tasks range from days to months and the compensation from tens to thousands of dollars.
-If we are to utilize these crowds then we shall have to experiment and see if we can get them accustomed to the crowdsourcing micro-tasks.
+If we are to utilize these crowds then we shall have to experiment and see if we can get them accustomed to the micro-tasks of crowdsourcing.
 This implies that we will have to effectively teach the crowd.
